%!TEX root = ../report.tex
\subsection{n-Grams} % (fold)
\label{sub:n_grams}

% subsection n_grams (end)

\subsection{Part of Speec (POS) Tagging} % (fold)
\label{sub:part_of_speec_}

One of the most fundamental parts of the linguistic pipeline is the part-of-speech (POS) tagging, a basic form of syntactic analysis which has countless applications in Natural Language Processing (NLP). We studied some of the best POS tagging tools \& settled on using Tweet NLP, a twitter specific POS tagger. We’ve used part-of-speech tagging as a feature for our task wherein every word/token in a given tweet is tagged based on its part-of-speech, some of which are twitter specific.

For our task, we selected 15 of the most common tags in linguistics (including the twitter specific tags). we made a count of the number of tagged tokens (with a confidence score > 0.9) in a tweet \& then used that as a feature.[rough work]

% subsection part_of_speec_ (end)

\subsection{Sentiment} % (fold)
\label{sub:sentiment}

We used \textit{SentiWordNet} to add features specifically related to the sentiment of the tweets. This is dictionary, designed for opinion mining, where each of the over 100,000 words is assigned a positive and negative sentiment score. For a given tweet, we calculate a positive sum feature: $p_{sum} = \sum_{i}^n p_i$ , where piis the positive sentiment score from SentiWordNet for the ith word in a tweet with n words. We similarly calculate a negative sum feature. If a word is not found in the dictionary, then it does not contribute to either of the two sentiment features. These two features are added to the bag of words feature vector as a real number. It is possible that different preprocessing steps could affect the sentiment score of a tweet by modifying said tweet (such as by stemming); future experimentation is required to determine the effects of different combinations of preprocessing on sentiment score.

% subsection sentiment (end)

\subsection{Irony} % (fold)
\label{sub:irony}

To account for possible irony in the tweets we implement two features based on the work of Reyes et. al [year]. The features are created to detect the so-called \textit{counter-factuality} and \textit{temporal compression} of a tweet. Reyes et. al. determined that ironic tweets were more likely to have a high level of these two measures.

\paragraph{Counter-factuality:} % (fold)
\label{par:counter_factuality_}
The first measure, counter-factuality, is focused on ``discursive terms that hint at opposition or contradiction in a text, such as about, nevertheless, nonetheless, and yet.'' (Citation). The full list of counter-factual words includes 41 entrees; there are a total of 4187 occurrences of these words in the data set, and 3123 tweets contain at least one counter-factual word.
% paragraph counter_factuality_ (end)

\paragraph{Temporal Compression:} % (fold)
\label{par:temporal_compression_}
The second measure of tweet irony that we considered is temporal compression, which focuses on words related to an opposition in time, thus indicating an abrupt change in narrative. (citation) The list of temporal compression words contains 13 words such as suddenly, abruptly, and now. There are only 170 instances of a temporal compression word in the dataset, with only 103 tweets even containing a single instance.
% paragraph temporal_compression_ (end)

\paragraph{Feature Creation:} % (fold)
\label{par:feature_creation_}
For each measure, we create a real-numbered feature based on the ratio of how many words in a given tweet possess the characteristic we are analyzing. That is, we have two ratio features $r_t = \frac{n_t}{n}$, where $t \in \left \{\ex{counterFactuality}, \ex{temporalCompression}\right \}$, $n_t$ is the number of words in a given tweet that fit into category $t$, and $n$ is the total number of words in the tweet.
% paragraph feature_creation_ (end)

% subsection irony (end)